---
title: "The basic R Markdown"
author: "Halef Caetano"
date: "1/10/2024"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data description
* Variable 1: salaries
* Variable 2: new_salaries 
* Variable 3: wide


# Data wrangling
* Step1: Install and load required packages
* Step2: Load the dataset
* Step3: Select columns of “rank”, “discipline”, “sex”, “salary”
* Step4: Filter the rows where “salary” is not missing value
* Step5: Group based on the required columns (“rank”,”discipline”, “sex”) and have the tally count of the rows
* Step6: Reshape the table from long to wide: using spread() to transfer the “sex” column to many more columns
based on the values in “sex”
* Step7: Reshape the table from wide to long: using gather() to combined multiple “sex” related columns( in
previous step6’s result) to one column “sex”

```{r, results=FALSE}
install.packages("tidyverse")
library(tidyverse)
library(readr)
Salaries <- read_csv("Module2/Salaries.csv")
View(Salaries)
new_salaries <- Salaries %>% select(rank, discipline, sex, salary) %>%
  filter(!is.na(salary)) 
group <- new_salaries %>% group_by(rank, discipline, sex) %>% 
  count() 
print(group)
wide <- group %>% spread(key = sex, value = n, fill = FALSE)   
final <- wide %>% gather(key = "sex", value = "n", -rank, na.rm = TRUE) %>% 
  separate(rank, into = "rank", sep = "_") 
print(final)
```

